\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-13 paper/draft.tex

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

Dialysis detects and scales out bottlenecked components by interposing on the application's module boundaries.
It is introduced as a backward-compatible, drop-in replacement of the language's module system.
It can be imported as an application-specific module (\eg \ttt{ignis} package) or can be bundled with a custom language runtime (\eg \sys-powered Lua) replacing its system-wide module system.
Dialysis starts by dynamically modifying the function that imports libraries: \eat{for locating and loading a module.}
  instead of simply locating and loading a module, the function yields to \sys, which applies a series of transformation steps to modules, with the goal of interposing on their boundaries.
We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
We next describe each one of these steps in more detail

@@

This section presents the design of 
% FIXME: add user data
At a high level, module dialysis works at three stages:

@@

@@

\section{Discussion and Limitations}
\label{diss}

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Language features used and their availability in other languages}.
    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
\toprule
                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
\midrule
Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
Walk objects                    &         &             &        &      &      &      &      &         \\
Shadow variables                &         &             &        &      &      &      &      &         \\
Wrap values                     &         &             &        &      &      &      &      &         \\
Global names                    &         &             &        &      &      &      &      &         \\
\bottomrule
\end{tabular*}
\label{tab:compatibility}
\vspace{-5mm}
\end{table}

\heading{Dynamic Language Interpretation}
Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.

>>>>

\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\tb}[1]{(Tab.\ref{tab:#1})}
\newcommand{\sys}{{\scshape Lya}\xspace}
\newcommand{\toy}{{\tt lya.js}\xspace}

@@

Dialysis starts by dynamically modifying the functionality of the module system that is responsible for importing and loading libraries:
  instead of simply locating a library in the filesystem and loading it, it yields control to \sys which applies a series of transformation steps to libraries, with the goal of interposing at their boundaries.
We start with a three-step overview of dialysis~\sx{overview}, highlighting the challenges that arise in the process.
We next describe each one of these steps in more detail~(\S\ref{one}--\ref{three}).

@@

% FIXME: add user data
At a high level, the goal of program dialysis is to \fra the program at the boundaries of third-party modules, apply transformations that insert analysis-specific machinery, and then carefully \ass individual components to maintain the original semantics.
 In more detail, these three phases are as follows:

@@

\sys's micro-benchmark suite was designed with two goals in mind.

The first goal was to test key properties of each analysis and confirm it outputs the expected results.
For example, to better understand performance diagnosis policy and confirm it works correctly, we craft a library that contains four other libraries with pre-defined bottlenecks.
The library can perform one of three operations, depending on its current state:
  (i) invoke a call to a module it imports,
  (ii) busy-wait, or
  (iii) respond to calls by returning a value.

The second goal was to identify understand \sys bottlenecks in a controlled environment, 
Both of these goals would have been difficult to achieve outside a synthetic environment, as we do not fully understand applications we haven't written ourselves.

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Synthetic Micro-benchmarks}.
		Applying the four analyses on a series of synthetic micro-benchmarks, created to stress different features.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
\toprule
              &   Base    &  SA     & PD       &   TIC    &   LSR     \\
\midrule
something1    &           &  0.70   &    3.43  &   3.46   &   3.26    \\
something2    &           &  1.31   &    4.81  &   4.55   &   4.63    \\
something3    &           &  5.95   &    4.78  &   4.25   &   4.85    \\
something4    &           &  18.29  &   11.20  &   10.24  &   9.54    \\
something5    &           &  24214  &   24721  &   24574  &   24502   \\
\bottomrule
\end{tabular*}
\label{tab:synthetic}
\vspace{-5mm}
\end{table}

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Applying \sys to single-library programs}.
		\fixme{Execution time of four test suites against }
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} ll lll}
\toprule
                    & Base   &  SA   & PD     &   TIC   & LSR     \\
\midrule
Classnames~\cite{}  &  2.72  & 6.62  &  6.61  &  6.10   & 5.94    \\
Debug~\cite{}       & 31.39  & 33.54 &  33.94 &  33.96  & 33.04   \\
% Minimist\\
~~~-t1              & 31.46  & 60.13 &  60.00 &  56.62  & 56.72   \\
~~~-t2              & 19.17  & 59.77 &  60.75 &  57.15  & 57.79   \\
~~~-t3              & 21.64  & 205.2 &  205.53&  132.25 & 137.84  \\
~~~-t4              & 20.69  & 59.70 &  60.75 &  59.92  & 56.60   \\
~~~-t5              & 20.49  & 70.48 &  72.20 &  64.71  & 66.03   \\
Moment~\cite{}      & 31.73  & 48.04 &  49.23 &  44.95  & 46.12   \\
yargs~\cite{}       & 13.42  & 13.00 &  14.41 &  13.47  & 13.48   \\
\bottomrule
\end{tabular*}
\label{tab:meso}
\vspace{-5mm}
\end{table}

Table~\ref{} depicts the results of the four analysis applied to these benchmarks.
We decided to report all combinations of analyses and benchmarks, but in practice not all are useful---\eg some modules do not feature interesting access or performance patterns.
Currently, these benchmarks return the results we expect, but they did help with the identification of problems such as 
These be
Load is visible at the application level (left), but the lack of detail does not help determine which modules must be scaled out.
Module-level data, collected by \sys' coordinator (right), reveal that \ttt{m3} receives the majority of the load.

To understand the costs of proxy interposition, we measure the time to access deeply-nested properties of two versions of an object:
  unmodified and proxy-wrapped.
Paths to the properties (\eg \ttt{a.b.c.$\ldots$}) are random but generated prior to running the experiment.
We construct 500MB-sized objects, each with a fanout of 8 fields nested for 12 levels.
The proxy-wrapped version introduces interposition at every level.
Traversing one million 12-edge paths (\ie root to leaves) averages 167.2ms and 595.7ms for the unmodified and proxy-wrapped versions, respectively.

We emphasize that this is an artificially constructed benchmark stressing worst-case overheads nowhere near an normal execution:
  for comparison, the transformation of these objects itself took nearly 16 seconds ($10^3\times$ more than what we experienced with real modules).
The takeaway is that \sys-inherent overheads due to interposition are unlikely to be the bottleneck of an analysis.

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Applying \sys to three large applications}.
		\fixme{Highlight some things}
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} lll}
\toprule
                    & Koa    & Moeda   &  Terminalizer \\
\midrule
 Size (KB)          & 41M    &  29M    &   262M        \\
 LoC                & 127K   &  79K    &   39K         \\
 Top-level modules  &  24    &  7      &    33         \\
 Total Modules      &  432   &  260    &    1084       \\
 Lya detects:       &  1507  &   729   &     2355      \\
 Baseline           &  xx    &         &               \\
 A1 (TF)            &        &         &               \\
 A3 (HF)            &        &         &               \\
 A8 (Types)         &        &         &               \\     
\bottomrule
\end{tabular*}
\label{tab:macro}
\vspace{-5mm}
\end{table}

Highly popular applications---for example, Koa.js and Terminalizer have 28.3K and 8.7K stars stars on GitHub, respectively.
Applying \sys to these applications generates much larger analayses
For example, the performance diagnosis analysis hooks reports timing characteristics for

The difference between the modules detected statically (by running \ttt{npm ls}) and the ones observed by \sys is due to a few different reasons.
One is that an analysis does not report accesses if a 
\sys analyzes modules that are part of the standard library too (some of which have themselves internal dependencies), which are not shown by \ttt{npm}.
Our post-processing counts by module name (\ie squashes duplicate reports by 
This can affect the results of multiple imports with the same name at different parts of the tree that would indeed correspond to different.
For example, importing two different versions of a library at two different parts of the dependency tree will result in to two different with the same name.
It also squashes cache entries that correspond to one module imported by multiple modules, which would create separate entries in \sys's augmented cache, but would result in a single count for Tab.~\ref{macro} (for \sys's treatment of the module cache, see~\S\ref{cache}).
Confirming that \sys performs correctly under these scenarios is one part of the motivation behind the synthetic micro-benchmarks shown earlier~\sx{micro}.

\section{Discussion}
\label{diss}

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Language features used and their availability in other languages}.
    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
\toprule
                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
\midrule
Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
Walk objects                    &         &             &        &      &      &      &      &         \\
Shadow variables                &         &             &        &      &      &      &      &         \\
Wrap values                     &         &             &        &      &      &      &      &         \\
Global names                    &         &             &        &      &      &      &      &         \\
\bottomrule
\end{tabular*}
\label{tab:compat}
\vspace{-5mm}
\end{table}

The techniques presented in this paper are applicable to any programming language.
We chose the JavaScript ecosystem to evaluate the feasibility of our approach, primarily because
  (i) it boasts the largest collection of libraries (and number of problems)~\cite{modulecounts} and
	(ii) we had prior experience by writing two systems that make extensive use of dynamic analysis---more sophisticated versions of analyses \fixme{XX} and \fixme{XX}.
In this section, we discuss the requirements for building \sys over other runtime environments.
% FIXME: All these features have to have been discussed earlier

By operating on library boundaries, program dialysis makes use of five key features available in a programming language~\tb{compat}.
All major programming languages can support these five features in a variety of ways, as described below.

First, \sys replaces the implementation of the import statement (\eg \ttt{require});
  this feature is important for compatibility reasons---otherwise developers would have to replace all import statements in a deeply nested tree.
If this is a function (\eg JavaScript, Scheme, Racket \etc) then replacement can be easily achieved by replacing its definition.
If this is a special-keyword statement such as \ttt{import}, this can be achieved by a rewriting rule that replaces import with a special function;
% This is simplified by the fact that the import syntax is trivial.

Second, \sys makes extensive use of weak maps to support to check for equality and, more frequently, for checking for cycles during object traversal (which requires equality).

Dynamic languages have features---\eg name (re-)binding, value introspection, dynamic code evaluation, and access interposition---that enable runtime transformations~\cite{aop, metaobject}.
They conveniently unify module identification with interposition: % used for performance monitoring and replica construction:
  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.

Other dynamic languages such as Lua, Ruby, and Python conveniently unify module identification with runtime interposition:
% used for performance monitoring and replica construction:
  a single function or function-like operator locates a module, interprets it, and applies transformations before exposing its interface in the caller context.
All these languages offer runtime capabilities such as name (re-)binding, value introspection, name interception, and access interposition.
% Languages such as Smalltalk and Lisp that treat ``everything'' as an object or a  function, need to interpose through object wrappers or function closures, respectively.

Compiled languages such as Haskell, OCaml, and Rust would apply transformations using compile-time metaprogramming facilities.
Examples include templates (\eg Template Haskell) and macro expansions (\eg Rust's macro system).
Such facilities would alleviate the runtime overhead of transformations, improving program startup times;
  however, they would not affect the overhead of contract evaluation, as this is still a runtime operation.
Static type checking could further aid developers by issuing warnings of incompatible privilege settings.
Contrary to OSMLC, there is no need for support from the runtime linker~\cite[\S VII]{breakapp:ndss:2018} because compartments do not execute as separate processes.
